---
title: "Extract ticket price from VVS Emails "
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
source("processfile.R")
source("findpattern.R")
source("make_email_list.R")
```

## Introduction
For the annual tax declaration, I wanted to find an automated way to find the total amount of money I have paid for online tickets. 
The code below workks for Online tickets from Stuttgart and Munich.
The mails were exported from my Mail-App.

## Read Data
```{r}
filepath <- "ssb2018.mbox/mbox"
rawtextlist <- processFile(filepath) 
head(rawtextlist)
```

## Parse Data
First we need to find thepoint were an email starts. 
The ticket price will be present multiple times in the email, also VAT. We only need one value per mail.
```{r}
mailstart <- "From ticketshop@ssb-ag.de"
#for the munich mvv it would be: "From ticketshop@mvv-muenchen.de"
#convert the emails in a list of strings
lll <-makeEmaiStringList(rawTextList = rawtextlist, starterStr = mailstart)
head(lll)
#find the values
erg <- lapply(lll, findValueInList)

```

## Result
And here it is:
```{r}
do.call(sum, erg)

```

