---
title: "Extract ticket price from VVS Emails "
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
library(stringr)
source("processfile.R")
source("findpattern.R")
source("make_email_list.R")
```

## Introduction
For the annual tax declaration, I wanted to find an automated way to find the total amount of money I have paid for online tickets. 
The code below workks for Online tickets from Stuttgart and Munich.
The mails were exported from my Mail-App.

## Read Data
```{r}
filepath <- "ssb2018.mbox/mbox"
rawtextlist <- processFile(filepath) 
head(rawtextlist)
```

## Parse Data
First we need to find thepoint were an email starts. Then we convert the emails in a list of strings. So every email is a one entry in a list.
The ticket price will be present multiple times in the email, also VAT. We only need one value per mail.
```{r}
#for the munich mvv it would be: "From ticketshop@mvv-muenchen.de"
mailstart <- "From ticketshop@ssb-ag.de"

emailStrinList <-makeEmaiStringList(rawTextList = rawtextlist, starterStr = mailstart)
head(emailStrinList)
```
### And now find the find the values
```{r}
erg <- lapply(emailStrinList, findValueInList)

```

## Result
And here it is:
```{r message=FALSE, warning=FALSE}
do.call(sum, erg)

```

